XXX

### 2012-02-23 paper/engNERwiki.tex
A tiny little change.

Proper entities that are not deemed NE by ConLL cause XXX little concern: they are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that we need no adjustment XXX to our original method.

>>>>

Proper entities that are not deemed NE under the ConLL scheme cause XXX little concern: they are either missing from DBpedia altogether, or we can map the classes they belong to to the NER category \texttt{0} (not an entity). This "ontological filtering" ensures that we need no adjustment XXX to our original method.
